Verification and Synthesis of Embedded Systems: \\ Advances and Challenges

### 2017-01-01 paper.tex
review Section "Incorporating System Models to Automated Verification and Synthesis Procedures"

Scratch is another example of a software model checker, which uses knowledge about the system to be verified and the underlying hardware, for detecting races related to direct memory access (DMA), in the Cell BE processor~\cite{Donaldson10}. That tool also uses BMC, in order to detect DMA races, and BMC with \textit{k}-induction, which aims to prove the absence of races. If support to other DMA operations were added, Scratch could be adapted to different architectures, {\it i.e.}, the same techniques would be employed, but with a different system behavior/knowledge.

>>>>

In this respect, DSVerifier has been extended to automatically synthesize digital stabilizing controllers for continuous plants~\cite{Abate17}. In particular, a counter-example guided inductive synthesis approach, implemented in a tool called digital system synthesizer (DSSynth), uses inductive synthesis in conjunction with DSVerifier's algorithm for verifying robust closed-loop stability that addresses plant variations as interval sets as well as FWL uncertainties in digital controllers. DSSynth is able to successfully synthesize stable digital controllers for a set of intricate plant models taken from the literature within minutes.

Apart from the control system domain, Scratch is another example of a software model checker, which uses knowledge about the system to be verified and the underlying hardware, for detecting races related to direct memory access (DMA), in the Cell BE processor~\cite{Donaldson10}. That tool also uses BMC, in order to detect DMA races, and BMC with \textit{k}-induction, which aims to prove the absence of races. If support to other DMA operations were added, Scratch could be adapted to different architectures, {\it i.e.}, the same techniques would be employed, but with a different system behavior/knowledge.
